---
title: "Orange Tree Growthing Prediction"
author: "Wayne Chan"
date: "2017-03-10"
output: 
  ioslides_presentation: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This was built for the course Developing Data Products as part of Data Science Specialization in Coursera.

The shiny app developed for this assignment is avalilable at: https://doost.shinyapps.io/shinyapp/

The source codes of ui.R and server.R and also Rpresentation are available on the GitHub repo: https://github.com/emamdoost/Developing_Data_Products


## Methodology

I will use a sample dataset named "Orange" in R datasets to formula a simple linear regression. The model generated from the regression will apply to later function of predition. While a user move the slider bar to select a value of days of orange tree growthing, it will estimate the predicted circumference of orange tree and show in the web page.


## Regression Modeling

```{r Orange, echo = TRUE}
summary(lm(circumference~age, Orange))
```

## Residual Plot of Regression 

```{r}
par(mfrow = c(2, 2))
plot(lm(circumference~age, Orange))
```

